---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metaSurvMissCI

<!-- badges: start -->

<!-- badges: end -->

This package include two functions: `impute_se_surv` and `forest_surv`. `impute_se_surv` impute missing precision information for meta analysis of survival rates and calculate survival rates and their SEs on the transformed scale. `forest_surv` provides a forest plot of the meta-analysis of survival rates.

For more information about each function, type `?impute_se_surv` and `?forest_surv`.

## Installation

You can install the development version of metaSurvMissCI from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kzkzmr/metaSurvMissCI")
```

## Example

```{r library, message = FALSE}
library(metaSurvMissCI)
library(meta)
```
```{r example, fig.width=10, fig.height=4}
data("metadata_chordomas")
impdata <- impute_se_surv(data = metadata_chordomas, St = "PFS5y",
                          LCL = "PFSL5y", UCL = "PFSU5y", n = "n",
                          nt = "n_5yPFS", ne = "ne_PFS", p = "pr_PFS")
meta_imp <- metagen(TE = tr_St, seTE = tr_SE, studlab = Study,
                     data = impdata, method.tau = "REML")
forest_surv(meta_imp, xlim = c(30, 100), estlab = "5-year PFS (%)")
```
